The classical mutual information in mean-field spin glass models

### 2015-12-16 prb_resub/referee_response/response.txt

RESPONSE:
========

	We thank the referee for the opportunity to clarify this point. The 
	definition of the mutual information is based on formula (2) in the 
	manuscript. Formula (2) is the standard definition of the classical 
	Renyi entropy, which in the limit $n\to 1$ become the Shannon entropy. 
	Formula (2) and the Shannon entropy can be used in systems that do not 
	have the notion of space and locality. The two subsystems A and B 
	appearing in (2) can be interpreted as two complementary groups of 
	spins, without any need for an underlying spatial bipartition. Thus, 
	the quantities that we address in our study, e.g., the mutual information, 
	are well-grounded from an information theoretical point of view. This 
	is now stressed in the introduction below formula (2) with the sentence

		" For local spin models the bipartition correspond to a spatial 
		separation between the spins. However, the definition~\eqref{renyi-intro} 
		can be used  in models with no notion of space, where it quantifies 
		the correlation between two groups of spins rathen than two spatial 
		regions."

	Moreover, (2) can be interpreted as ratios of partition functions defined 
	on the booklet. This is an exact correspondence, and it is not related to 
	any notion of locality. To clarify this point we now demonstrate explicitly 
	the equivalence between the booklet construction and (2) in the beginning of 
	section 2. From the derivation it is clear that the booklet construction 
	is meaningful also in mean-field models.

	A further direct check is provided in appendix B where we discuss (following 
	the referee suggestion) the classical Renyi entropy and the mutual information 
	for the infinite-range clean (i.e., without disorder) Ising model. For instance, 
	in Figure 12 and Figure 13 the continuous lines are obtained using the booklet 
	construction, while the symbols (rhombi) are the results using the definition 
	of the classical Renyi entropy and mutual information (formulas (2) and (4) 
	in the manuscript). The agreement, apart for finite-size corrections, 
	confirms the applicability of the booklet construction for infinite-range 
	models.

@@

REFEREE:
-------

	Is there any other work treating the booklet geometry in mean field 
	systems? For example, what is obtained for the simple, pure Ising model 
	with infinite-range interaction?

RESPONSE:
========

	We would like to thank the referee for this very useful comment. The only study we 
	are aware of is in

@@

		J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P01023 (2012)

	In this work the authors investigate the mutual information in the Lipkin-Meshkov-Glick 
	(LMG) model. In particular, they provide results for the case with zero magnetic field, 
	where the model becomes equivalent to a classical infinite-range Ising model. However, 
	the authors investigate the standard mutual information which is obtained from the 
	Shannon entropy, instead of the classical Renyi one.

	In contrast with our results the authors find that the Shannon mutual information is 
	finite at any temperature except at the critical point where it diverges logarithmically.

	Motivated by the referee observation and the results of Wilms et al we now discuss 
	in the new version of the manuscript the Renyi entropy and mutual information in the 
	clean infinite-range Ising model (in appendix B). We find that, in constrast with the 
	Shannon mutual information, the Renyi one exhibits a volume law for any temperature, 
	similar to our result for the S-K model. Moreover, I_2 exhibits intriguing subleading 
	(i.e., subextensive) contributions. Specifically, we numerically observe that these 
	corrections are logarithmically divergent with system size N. Moreover, they are 
	present at three values of the inverse temperature. Their precise behaviors is given 
	as

		beta=1/2     ---->  1/4 log(N)

		beta=1/(1+w) ---->  1/2 log(N)

		beta=1	     ---->  1/2 log(N)

	Notice that beta=1/(1+w) corresponds to the critical temperature on the 2-sheets 
	booklet with aspect ratio w.

	These new results raise the question whether similar subleading corrections are 
	present in the S-K model, as also noticed by the referee. Importantly, it would be 
	interesting to determine the prefactor of these logarithmic corrections to check 
	whether they are affected by the disorder. However, one should notice that to 
	investigate analytically this issue one should go beyond the saddle point 
	approximation, which at least in the low-temperature regioon requires knowing the 
	full replica-symmetry-broken solution of the model.

	Another possibility is to focus at beta=1/2 where, in analogy with the clean case, 
	a logarithmic correction is expected and where the high-temperature replica symmetric 
	result fully captures the saddle point behavior. The strategy would be to consider the 
	deviations from the saddle point in the Monte Carlo data. However, we checked that 
	our numerical results are not precise enough to determine the corrections and further 
	numerical effort would be needed to clarify this point.

@@

		J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P010011 (2011)

REFEREE:
-------
	(2). The definition of the mutual information in the present case is
	not clear for me. Please describe how to define and calculate S(B) and
	S(A or B) in the SK model.

RESPONSE:
========

	We thank the referee for this useful comment. Eq. (2), and later Eq. (5) via the replica 
	trick, are both quite explicit. Combined with Eq. (4) they give the mutual information in 
	the SK model. The non-locality of the interactions does not affect the definition compared 
	with the usual one for local models. The definition of region A is however less obvious, 
	and in the case of this work, we simply take it as an arbitrary set of points, rather than 
	one that is spatially connected. As it is clear from the manuscript the best way to calculate 
	the mutual information is using (4) calculating the three different contributions S(A) S(B) 
	and S(AUB) separately. These correspond to ratios of partition functions on the booklet with 
	different aspect ratio w. In particular, S(AUB) is obtained from the ratio Z(w=1)/Z(w=0). 
	As this was not clearly stated in the manuscript we now have written it explicitly in 
	section 2

@@

REFEREE:
-------

	(3). The authors summarized that the entropy is proportional to the system size by using the 
	numerical analysis. Since the entropy is calculated from the logarithm of the partition function, 
	the result looks trivial for me. As far as I understand, the subleading term is	important to find 
	the boundary law behavior in the local (non mean-field) models. (The leading term is canceled out 
	by the definition of the mutual information). Do the authors consider that the subleading term is 
	not important in the present system? I expect that some universal properties exist in the subleading 
	terms.

RESPONSE:
========

	We agree that in general the leading term is proportional to the system size is an obvious result. 
	In the manuscript we report the entropy only as a sanity check of our calculations.  We also agree 
	that it is likely that the subleading terms contain more universal information. We thank the referee 
	for raising this point. Although the analytical calculation of the subleading corrections to the entropy 
	and the mutual information is possible in principle, it requires going beyond the saddle point approximation 
	described in section III C. This should be straightforward in the paramagnetic phase although it would 
	require a considerable amount of work below the critical point. Notice that the same problem of 
	calculating saddle point corrections is challenging in the regular SK model. We think that this goes 
	beyond the scope of the paper and it is suitable for future work.

@@

REFEREE:
-------

	(4). The authors study the aspect-ratio dependence of the result closely. It is clearly understood that 
	the limits omega=0 and 1 reduces to the standard results. This means that we can find a result interpolating 
	their limits in the present problem. I do not expect any interesting behavior between the limits. What 
	did the authors expect as the result and what do the authors consider the obtained results interesting, 
	other than the crossing behavior?

RESPONSE:
========

	We agree that omega=0 and 1 are trivial results, at least in the standard SK model, and that one would 
	expect that the results between these two points should vary smoothly, and this is reflected in our data. 
	However, different aspect ratios omega are needed in the booklet constructions in order to construct the 
	mutual information. We should also stress that the functional dependence of the mutual information on 
	omega is not trivial. The same statement of the referee would apply to local models. However, as it is clear 
	from Ref [29], the shape function of the mutual information contains universal behavior if the 
	parent model is critical and described by a conformal field theory. In that respect, we believe it was 
	worth examining the aspect ratio behavior in the SK model. Notice that this functions have been also 
	investigated in clean (withoud disorder) mean field models in

		O. Cohen, V. Rittenberg, T. Sadhu J Phys A 48 055002 (2015)

@@

REFEREE:
-------

	(5). This comment is related to the previous one (4). Strictly
	speaking, I do not see any surprising behavior in the result. What is
	the significance of the present study? Did the authors find anything
	on the information properties of the SK model?

RESPONSE:
========

	From our answer to point 1) it should be clear now that our work is well grounded from the information 
	point of view as we are studying the standard classical Renyi entropies and mutual information. These 
	quantities have been shown to contain universal information for instance in local critical models described 
	a conformal field theory (Ref. [29]). Again, we should stress that their behavior in disordered and glassy systems has 
	not been investigated in the previous literature. We chose to focus on the SK model which is one of the few 
	exactly solved models for spin glasses and the base case for understanding glassy behavior, and its solution, 
	although the model is mean field, exhibits quite complex features.

	We have found that the Renyi entropy S_2 and the mutual information I_2 have a volume law and we provided analytical 
	results using the saddle point approximation. This can be consired as a zeroth order starting point because, as 
	correctly observed by the referee and as clear from our results on the clean infinite range Ising model (appendix B), 
	further interesting information could be contained in the finite-size effects. However, already the saddle point 
	results for S_2 and I_2 are non trivial since they reflect the replica symmetry breaking pattern of the solution 
	of the SK model. We should stress that we only provided the 1-RSB approximation for these quantities. The fact that 
	the 2-RSB is necessary at low temperatures confirms the fact that our results are interesting.

	Our results are essential in order to go beyond the saddle point, studying subextensive correctins in S_2 and I_2. 
	This is confirmed by the results that we provide in appendix B where we show that already for the clean infinite 
	range Ising model the mutual information contains logarithmically divergent (with system size) terms which reflect 
	critical behaviors. Our work raises the important question as to whether such subextensive contributions are present 
	at glassy transitions. Moreover, a related interesting question is if disorder renormalizes the prefactor of this 
	logarithmic behavior. Additionally, for the SK model it is interesting to understand whether the replica-symmetry-breaking 
	mechanism affects this prefactor. Besides being interesting in their own, our results are necessary in order to 
	understand the subleading  of S_2 and I_2.

@@

REFEREE:
-------

	(6). The authors only focused on the result at n=2. It would be	interesting if the authors mention the n-dependence of 
	the result. Especially, the limit n=1 would give a nontrivial result and is interesting. I expect that it wouldn't 
	be difficult to analyze the replica symmetric solution.

RESPONSE:
========

	We thank the referee for asking about this point. In fact we thought about investigating the analytic continuation 
	n->1 to obtain the Shannon Renyi entropy and mutual information. The referee question is interesting especially 
	especially in order to compare with the results for the clean infinite range Ising model obtained in Wilms et al. 
	It has been shown in fact in ... that the Shannon mutual information is O(1) (i.e., not extensive) at any temperature 
	except for the critical point at beta=1 whete it diverges logarithmically with system size.

	Following the referee suggestion we now provide results for the analytic continuation n->1. First, one should observe 
	that in the limit of infinite temperature one has from formula () in our paper that

	   I_n(beta)/N = beta^2 omega(1-omega)n/2    for beta --> 0

	which implies that

	   I_1/N = beta^2 omega(1-omega)/2

	i.e., the Shannon entropy obeys a volume law in the paramagnetic phase. This is in contrast with the result in the 
	clean Ising reported in Wilms et al and it is apparently an effect of the disorder. This suggests that the subextensive 
	behavior for I_1 found for the clean system is an effect of fine tuned cancellations that do not happen in presence of 
	disorder.

	In the paper we now included the saddle point equation in the high-temperature phase (equation (31)).

@@

REFEREE:
-------

	(7). Although the manuscript is written very clearly, it is somewhat
	too long. For example, the authors summarized the results in the
	introduction, and they are described again in the final section. It is
	not necessary to summarize the results in the introduction.

RESPONSE:
========

	We would like to thank the referee for this useful comment. We now 
	summarize the main results of the paper in the conclusions and not in the 
	introduction, while in the introduction we stress better the physical motivation 
	and the results of the work.

### 2015-12-16 sk_model_v20.tex
16/12/2015

(\omega,n,\beta)]/\partial q_0=0$. For the $2$-sheets booklet (i.e., $n=2$) this is  

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure*}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/I2_MC_v1}
%\includegraphics*[width=0.93\linewidth]{./I2_MC_v1}
\caption{The classical disorder-averaged mutual information per spin $[{\mathcal I}_2]/N$ 
 in the S-K model on the $2$-sheets booklet: 
 $[{\mathcal I}_2]/N$ versus the inverse temperature $\beta$. The 
 different panels correspond to different booklet ratios $\omega=1/2,1/4,1/8$ 
 (see Fig.~\ref{cartoon}). The same scale is used on both axes in all 
 panels. The symbols are the Monte Carlo data for systems with $N=32,64,128$ 
 spins per sheet. The Monte Carlo error bars are smaller than the symbol size. 
 The dash-dotted line is the analytical result in the replica-symmetric (RS) 
 approximation.  
}
\label{I2-MC}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The dash-dotted line in the Figure denotes the analytical result $[S_2^{RS}]$ obtained within 
the RS approximation (see section~\ref{rs-section}). More precisely, $[S_2^{RS}]/N$ is obtained 
from Eq.~\eqref{renyi} and the expression for the free energy $[F_{RS}]$ (cf. Eq.~\eqref{rs-F}). 
Notice that in the high-temperature limit $\beta\to0$, where the RS approximation is exact, 
Eq.~\eqref{renyi} and Eq.~\eqref{ht-logZ} give 
%
\begin{equation}
\frac{[S^{RS}_2]}{N}=\omega\log(2)-\frac{\beta^2}{4}\omega^2+{\mathcal O}(\beta^3).
\end{equation}
%
From Fig.~\ref{Renyi-MC} one has that the extrapolated MC data are in quantitative 
agreement with $[S_2^{RS}]/N$ for $\beta\lesssim 1.5$, whereas strong deviations are 
observed at lower temperatures (not shown in the Figure). A better approximation for 
$[S_2]/N$ at low temperatures is obtained by including the effects of the replica 
symmetry breaking. The circles in Fig.~\ref{Renyi-MC} denote the one-step replica 
symmetry breaking result $[S_2^{1\textrm{-}RSB}]/N$ (see section~\ref{rsb-1-section}), 
which is obtained from Eq.~\eqref{renyi}  and Eq.~\eqref{RSB-1-logZ}. Remarkably, 
$[S_2^{1\textrm{-}RSB}]/N$ is in excellent agreement with the extrapolated Monte Carlo 
data for $\beta\lesssim 2$.

@@

Figure~\ref{I2-MC} plots $[{\mathcal I}_2]/N$ versus $0\le\beta\le 2.5$ and $\omega=1/2,1/4,
1/8$ (panels from left to right in the Figure). Notice that by definition (cf. Eq.~\eqref{MI}) 
$[{\mathcal I}_n(\omega)]=[{\mathcal I}_n(1-\omega)]$. Circles, squares, and triangles  
are Monte Carlo data for $N=32,64,128$. In the high-temperature region $[{\mathcal I}_2]$ 
exhibits a vanishing behavior. Moreover, finite-size effects are ``small''. Using Eq.~\eqref{logZ-ht} 
it is straightforward to derive the high-temperature behavior of $[{\mathcal I}_n]$ as  
%
\begin{equation}
[{\mathcal I}_n]=\frac{N\beta^2}{2}\omega(1-\omega)n+{\mathcal O}
(\beta^4).
\end{equation}
%
$[{\mathcal I}_2]/N$ increases upon lowering the temperature up to $\beta\approx 1$, where 
it exhibits a maximum.  
One should stress that its position is not simply related to the paramagnetic-glassy transition. 
Furthermore, the data for $[{\mathcal I}_2]/N$ at different system sizes do not exhibit any crossing. 
This is in sharp contrast with local models~\cite{jaconis-2013}, where ${\mathcal I}_n/L$ exhibits a 
crossing at a second order phase transition. The dash-dotted line in Fig.~\ref{I2-MC} is the 
analytical result obtained using the replica symmetric (RS) approximation (see 
section~\ref{rs-section}). Formally, this is obtained using Eq.~\eqref{MI} and Eq.~\eqref{rs-F}, 
and it is in perfect agreement with the MC data in the whole paramagnetic phase.

Interestingly, at low temperatures $[{\mathcal I}_2]/N$ exhibits strong finite-size corrections, 
and significant deviations from the RS result. In order to extract the thermodynamic behavior of 
$[{\mathcal I}_2]/N$ we fit the MC data to 
%
\begin{equation}
\frac{[{\mathcal I}_2]}{N}=a+\frac{b}{N^{\phi}},
\end{equation}
%
where we fix $\phi=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated}.  
Different symbols now correspond to different aspect ratios $\omega$. Remarkably, the RS 
approximation (dash-dotted lines) is in good agreement with the extrapolations for $\beta\lesssim 0.6$. 
We should stress that in the region $0.6\lesssim\beta\lesssim 1$, i.e., near the peak, due to the large 
error bars it is difficult to reach a conclusion on the validity of the RS approximation. 
In particular, the data exhibit a systematic shift of the mutual information 
peak towards lower temperatures. Much larger system sizes would be needed to clarify this 
issue. The effect of the replica symmetry breaking, however, 
should be negligible. For instance, at $\beta=0.6$ for $\omega=1/2$ one can estimate that 
$|[{\mathcal I}_2^{RS}]-[{\mathcal I}_2^{1\textrm{-}RSB}]|/N\sim 2\cdot 10^{-5}$. Finally, clear deviations 
from the RS result occur at lower temperatures. For instance, for $\omega=1/8$, the numerical results 
exhibit deviations from the RS result already at $\beta\gtrsim 1$. 
These deviations, however, have to be attributed to the physics of the replica symmetry breaking. 
The full rhombi in Fig.~\ref{I2-extrapolated} denote the one-step replica symmetry breaking result 
$[{\mathcal I}_2^{1\textrm{-}RSB}]$, which is obtained using Eq.~\eqref{MI} and Eq.~\eqref{RSB-1-logZ}). 
The agreement between $[{\mathcal I}_2^{1\textrm{-}RSB}]$ and the Monte Carlo data is perfect 
up to $\beta\lesssim 2$.

@@

Here we discuss the R\'enyi entropy $S_2$ and the associated mutual information 
${\mathcal I}_2$ in the infinite-range Ising model without disorder defined by 
the hamiltonian 
%
\begin{equation}
\label{is-clean}
{\mathcal H}=-\frac{J}{N}\sum\limits_{i<j}S_iS_j+h\sum_i S_i.
\end{equation}
%
We consider the situation without external magnetic field, i.e., $h=0$ and 
fix $J=1$.

@@

%##########################################################################
\subsection{R\'eny entropy and mutual information: Exact treatment}

@@

The partition function of the model on a single sheet is given as 
%
\begin{equation}
Z(\beta)\equiv\textrm{Tr}\rho=\sum\limits_{p=0}^NB(N,p)e^{N\beta(\frac{p}{N}-
\frac{1}{2})^2},
\end{equation}
%
where $\rho\equiv 1/Ze^{-\beta {\mathcal H}}$ is the thermal density matrix. 
Given a bipartition of the spins into two groups $A$ and $B$ containing $N_A$ 
and $N-N_A$ spins, respectively, the reduced density matrix for $A$ is obtained 
as~\cite{wilms-2012} 
%
\begin{equation}
\rho_A\equiv\frac{1}{Z}\textrm{Tr}_B\sum\limits_{p,i}e^{N(\beta\frac{p}{N}-
\frac{1}{2})^2}|p,i\rangle\langle p,i|. 
\end{equation}
%
By performing the trace over part $B$ one obtains 
%
\begin{equation}
\rho_A=\sum\limits_{p_A,i_A}R(p_A)|p_A,i_A\rangle\langle p_A,i_A|,
\end{equation}
%
where $|p_A,i_A\rangle$ form a basis for part $A$ of the system and 
%
\begin{equation}
R(p_A)\equiv\frac{1}{Z}\sum\limits_{p_B=0}^{N-N_A}B(N-N_A,p_B)e^{N\beta
(\frac{p_A}{N}+\frac{p_B}{N}-\frac{1}{2})^2}.
\end{equation}
%

>>>>

(\omega,n,\beta)]/\partial q_0=0$. The saddle point equation reads 
where we used that 
\frac{1}{\sqrt{2\pi}}\int Dz\cosh^n(z\sqrt{q_0}\beta)= 
\frac{1}{2}\Gamma(n,n/2)\\
+\frac{1}{2^{n-1}}\sum\limits_{k=0}^{\frac{n}{2}-1}\frac{\Gamma(n+1)}
{\Gamma(k+1)\Gamma(n-k+1)}e^{2\beta^2 q_0 \big(\frac{n}{2}-k\big)^2}
For the $2$-sheets booklet (i.e., $n=2$) this is  

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure*}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/I2_MC_v1}
%\includegraphics*[width=0.93\linewidth]{./I2_MC_v1}
\caption{The classical disorder-averaged mutual information per spin $[{\mathcal I}_2]/N$ 
 in the S-K model on the $2$-sheets booklet: 
 $[{\mathcal I}_2]/N$ versus the inverse temperature $\beta$. The 
 different panels correspond to different booklet ratios $\omega=1/2,1/4,1/8$ 
 (see Fig.~\ref{cartoon}). The same scale is used on both axes in all 
 panels. The symbols are the Monte Carlo data for systems with $N=32,64,128$ 
 spins per sheet. The Monte Carlo error bars are smaller than the symbol size. 
 The dash-dotted line is the analytical result in the replica-symmetric (RS) 
 approximation. In (a) the dotted line is the result for the clean, i.e., without 
 disorder, infinite-range Ising model. 
}
\label{I2-MC}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The dash-dotted line in the Figure denotes the analytical result $[S_2^{RS}]$ obtained within 
the RS approximation (see section~\ref{rs-section}). More precisely, $[S_2^{RS}]/N$ is obtained 
from Eq.~\eqref{renyi} and the expression for the free energy $[F_{RS}]$ (cf. Eq.~\eqref{rs-F}). 
Notice that in the high-temperature limit $\beta\to0$, where the RS approximation is exact, 
Eq.~\eqref{renyi} and Eq.~\eqref{ht-logZ} give 
%
\begin{equation}
\frac{[S^{RS}_2]}{N}=\omega\log(2)-\frac{\beta^2}{4}\omega^2+{\mathcal O}(\beta^3).
\end{equation}
%
From Fig.~\ref{Renyi-MC} one has that the extrapolated MC data are in quantitative 
agreement with $[S_2^{RS}]/N$ for $\beta\lesssim 1.5$, whereas strong deviations are 
observed at lower temperatures (not shown in the Figure). A better approximation for 
$[S_2]/N$ at low temperatures is obtained by including the effects of the replica 
symmetry breaking. The circles in Fig.~\ref{Renyi-MC} denote the one-step replica 
symmetry breaking result $[S_2^{1\textrm{-}RSB}]/N$ (see section~\ref{rsb-1-section}), 
which is obtained from Eq.~\eqref{renyi}  and Eq.~\eqref{RSB-1-logZ}. Remarkably, 
$[S_2^{1\textrm{-}RSB}]/N$ is in excellent agreement with the extrapolated Monte Carlo 
data for $\beta\lesssim 2$. Finally, for comparison we report in panel (c) the analytical 
result (dotted line) for $S_2/N$ for the infinite-range Ising model without 
disorder at $\omega=1/4$ (see Appendix~\ref{clean-is}).

@@

Figure~\ref{I2-MC} plots $[{\mathcal I}_2]/N$ versus $0\le\beta\le 2.5$ and $\omega=1/2,1/4,
1/8$ (panels from left to right in the Figure). Notice that by definition (cf. Eq.~\eqref{MI}) 
$[{\mathcal I}_n(\omega)]=[{\mathcal I}_n(1-\omega)]$. Circles, squares, and triangles  
are Monte Carlo data for $N=32,64,128$. In the high-temperature region $[{\mathcal I}_2]$ 
exhibits a vanishing behavior. Moreover, finite-size effects are ``small''. Using Eq.~\eqref{logZ-ht} 
it is straightforward to derive the high-temperature behavior of $[{\mathcal I}_n]$ as  
%
\begin{equation}
[{\mathcal I}_n]=\frac{N\beta^2}{2}\omega(1-\omega)n+{\mathcal O}
(\beta^4).
\end{equation}
%
$[{\mathcal I}_2]/N$ increases upon lowering the temperature up to $\beta\approx 1$, where 
it exhibits a maximum.  
One should stress that its position is not simply related to the paramagnetic-glassy transition. 
Furthermore, the data for $[{\mathcal I}_2]/N$ at different system sizes do not exhibit any crossing. 
This is in sharp contrast with local models~\cite{jaconis-2013}, where ${\mathcal I}_n/L$ exhibits a 
crossing at a second order phase transition. The dash-dotted line in Fig.~\ref{I2-MC} is the 
analytical result obtained using the replica symmetric (RS) approximation (see 
section~\ref{rs-section}). Formally, this is obtained using Eq.~\eqref{MI} and Eq.~\eqref{rs-F}, 
and it is in perfect agreement with the MC data in the whole paramagnetic phase.  
Finally, we should stress that similar qualitative behavior is observed for ${\mathcal I}_2/N$ 
in the infinite-range Ising model without disorder. The analytical result for ${\mathcal I}_2/N$ 
at $\omega=1/2$ in the thermodynamic limit is reported in panel (a) (dotted line).

Interestingly, at low temperatures $[{\mathcal I}_2]/N$ exhibits strong finite-size corrections, 
and significant deviations from the RS result. In order to extract the thermodynamic behavior of 
$[{\mathcal I}_2]/N$ we fit the MC data to 
%
\begin{equation}
\frac{[{\mathcal I}_2]}{N}=a+\frac{b}{N^{\phi}},
\end{equation}
%
where we fix $\phi=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated}.  
Different symbols now correspond to different aspect ratios $\omega$. Remarkably, the RS 
approximation (dash-dotted lines) is in good agreement with the extrapolations for $\beta\lesssim 0.6$. 
We should stress that in the region $0.6\lesssim\beta\lesssim 1$, i.e., near the peak, due to the large 
error bars it is difficult to reach a conclusion on the validity of the RS approximation. 
In particular, the data exhibit a systematic shift of the mutual information 
peak towards lower temperatures. Much larger system sizes would be needed to clarify this 
issue. The effect of the replica symmetry breaking, however, 
should be negligible. For instance, at $\beta=0.6$ for $\omega=1/2$ one can estimate that 
$|[{\mathcal I}_2^{RS}]-[{\mathcal I}_2^{1\textrm{-}RSB}]|/N\sim 2\cdot 10^{-5}$. 
Moreover, the results for the infinite-range clean Ising (see Appendix~\ref{is-clean}) suggest 
that logarithmic scaling corrections as $\propto\log(N)/N$ could be present at criticality making 
the extrapolation to the thermodynamic limit tricky. 
Finally, clear deviations 
from the RS result occur at lower temperatures. For instance, for $\omega=1/8$, the numerical results 
exhibit deviations from the RS result already at $\beta\gtrsim 1$. 
These deviations, however, have to be attributed to the physics of the replica symmetry breaking. 
The full rhombi in Fig.~\ref{I2-extrapolated} denote the one-step replica symmetry breaking result 
$[{\mathcal I}_2^{1\textrm{-}RSB}]$, which is obtained using Eq.~\eqref{MI} and Eq.~\eqref{RSB-1-logZ}). 
The agreement between $[{\mathcal I}_2^{1\textrm{-}RSB}]$ and the Monte Carlo data is perfect 
up to $\beta\lesssim 2$.

@@

Here we discuss the R\'enyi entropy $S_2$ and the associated mutual information 
${\mathcal I}_2$ in the infinite-range Ising model without disorder, i.e., the 
Curie-Weiss (CW) model, defined by the hamiltonian 
%
\begin{equation}
\label{is-clean}
{\mathcal H}=-\frac{J}{N}\sum\limits_{i<j}S_iS_j+h\sum_i S_i.
\end{equation}
%
We consider the situation without external magnetic field, i.e., $h=0$ and 
fix $J=1$. The phase diagram of the model exhibits a paramagnetic phase at 
high temperature, while at low temperatures there is ferromagnetic order. The 
two phases are separated by a phase transition at $\beta_c=1$.
We consider both the situations with finite $N$ as well as the 
thermodynamic limit. For finite $N$ we provide exact numerical results for 
$S_2$ and ${\mathcal I}_2$, while we address the thermodynamic limit using 
the booklet construction and the saddle point approximation.

Similar to the S-K model, we find that the para-ferro transition persists on 
the booklet, and the critical temperature depends on the booklet ratio 
$\omega$. The R\'enyi entropy $S_2$ and the mutual information ${\mathcal 
I}_2$ are extensive, and their densities $S_2/N,{\mathcal I}_2/N$ finite 
and smooth at any temperature. Notice that this in constrast with what is 
obtained for the von Neumann mutual information~\cite{wilms-2012} ${\mathcal I}$, 
which is {\it finite} (i.e., ${\mathcal I}\sim {\mathcal O}(1)$) in the whole phase 
diagram, except for a logarithmically divergent behavior at the critical 
point at $\beta_c=1$.

However, information about the phase transition is encoded in the subleading, 
i.e. $o(N)$, corrections of ${\mathcal I}_2$. Precisely, logarithmically 
divergent corrections are present at $\beta=1/2,1$ and $\beta=\beta_c(\omega)$, 
with $\beta_c(\omega)$ the critical temperature of the model on the booklet 
with aspect ratio $\omega$.

@@

%##########################################################################
\subsection{R\'enyi entropy and mutual information: Exact treatment}

@@

The partition function of the model is given as 
%
\begin{equation}
Z(\beta)\equiv\textrm{Tr}\rho=\sum\limits_{p=0}^NB(N,p)e^{2N\beta(\frac{p}{N}-
\frac{1}{2})^2},
\end{equation}
%
where $\rho\equiv 1/Ze^{-\beta {\mathcal H}}$ is the thermal density matrix. 
Similarly, one has 
%
\begin{equation}
\label{rhon}
Z^n(\beta)\equiv\textrm{Tr}\rho^n=\sum\limits_{p=0}^NB(N,p)e^{2nN\beta(\frac{p}{N}-
\frac{1}{2})^2}. 
\end{equation}
%
Given a bipartition of the spins into two groups $A$ and $B$ containing $N_A$ 
and $N-N_A$ spins, respectively, the reduced density matrix for $A$ is obtained 
as~\cite{wilms-2012} 
%
\begin{equation}
\rho_A\equiv\frac{1}{Z}\textrm{Tr}_B\sum\limits_{p,i}e^{2N\beta(\frac{p}{N}-
\frac{1}{2})^2}|p,i\rangle\langle p,i|. 
\end{equation}
%
By performing the trace over part $B$ one obtains 
%
\begin{equation}
\label{rhoA}
\rho_A=\sum\limits_{p_A,i_A}R(p_A)|p_A,i_A\rangle\langle p_A,i_A|,
\end{equation}
%
where $|p_A,i_A\rangle$ form a basis for part $A$ of the system and 
%
\begin{equation}
R(p_A)\equiv\frac{1}{Z}\sum\limits_{p_B=0}^{N-N_A}B(N-N_A,p_B)e^{2N\beta
(\frac{p_A}{N}+\frac{p_B}{N}-\frac{1}{2})^2}.
\end{equation}
%
From~\eqref{rhoA} it is straightforward to obtain 
%
\begin{equation}
\label{trrhoA}
\textrm{Tr}\rho_A^n=\sum\limits_{p_A=0}^{N_A}B(N_A,p_A)R^n(p_A). 
\end{equation}
%
Similarly, $\textrm{Tr}\rho^n_B$ is obtained from~\eqref{trrhoA} substituting 
$A\to B$ and $N_A\to N-N_A$, while $\textrm{Tr}\rho^n_{A\cup B}\equiv\textrm{Tr}
\rho^n$ is given in~\eqref{rhon}. The R\'enyi entropies $S_n$ and the mutual 
informations ${\mathcal I}_n$ can be numerically constructed numerically 
using~\eqref{trrhoA}, \eqref{rhon} and the definitions~\eqref{renyi-intro}
\eqref{MI}. The numerical results for $S_2$ and ${\mathcal I}_2$ for a system with 
$N=400$ spins are shown in Figure~\ref{renyi_clean} and Figure~\ref{mi_clean}, and 
are in good agreement with the saddle point results.

Figure~\ref{sp_corr} focuses on the finite-size corrections to the saddle point 
result for ${\mathcal I}_2$. We plot ${\mathcal I}_2-{\mathcal I}^{(sp)}_2$, with 
${\mathcal I}_2^{(sp)}$ denoting the saddle point results (see Figure~\ref{mi_clean}), 
versus $\beta$. We restrict ourselves to the situation with $\omega=N_A/N=1/2$, although 
similar resutls are expected at different $\omega$. Clearly, ${\mathcal I}_2-
{\mathcal I}_2^{(sp)}$ is vanishing at high temperature, whereas one has ${\mathcal I}_2-
{\mathcal I}_2^{(sp)}\to\log(2)$ in the limit $\beta\to\infty$ (horizontal line). 
Surprisingly, ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ diverges in the thermodynamic limit 
for $\beta=1/2,2/3,1$ (vertical lines in the Figure), which are the critical 
temperatures for the model on a booklet with $\omega=1,1/2,0$.

This divergence is logarithmic with $N$ as confirmed in Figure~\ref{clean_log} plotting 
$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|$ versus $\log(N)$ for fixed $\beta=1/2,2/3,1$. 
Interestingly, the precise behavior depends on $\beta$. Specificaly, one has 
$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/4\log(N)$ for $\beta=1/2$ and 
$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/2\log(N)$ for $\beta=2/3$ and 
$\beta=1$. Notice that this is dramatically different for the von Neumann mutual 
information ${\mathcal I}=\lim_{n\to 1}{\mathcal I}_n$, which exhibits only one 
divergent peak at $\beta=1$~\cite{wilms-2012}.
